Maxwell's Silver Hammer, briefly:\\ On the application of pulsed microwave acoustic resonant viral inactivation

### 2020-07-23 documents/pamphlet.tex
Pamphlet

\documentclass[fleqn,10pt]{article}

@@

Brief: Pulsed microwave-acoustic resonant virus inactivation

Note: please doubt

Mechanism

Evidence for effectiveness:

Evidence against effectiveness:

@@

Tasks

Implementation guide

Results seem to indicate that any region with an electric field strength greater than 150 V/m between for 10 ns will be sterilized.

>>>>

\documentclass[fleqn,10pt]{paper}

\usepackage[left=2cm,right=2cm,
top=0cm,
bottom=2.25cm,%
headheight=11pt,%
letterpaper]{geometry}

\include{preamble}

\title{Maxwell's Silver Hammer, briefly:\\ On the application of pulsed microwave acoustic resonant viral inactivation}

@@

\maketitle

%\footnote{The}

This is a heavily condensed version of a (hideously unfinished) paper at \href{https://www.github.com/0xDBFB7/covidinator/documents/paper.pdf}{\faGithub/0xDBFB7/covidinator}.

I think it is important that you doubt and scrutinize everything written. This hinges on minutia and

{\Large \textbf{The mechanism}}

The literature is littered with irreproducible claims of non-thermal effects; however, this certainly appears to be a singular anomaly.

\cite{Microwave2009} \textrightarrow \ (\cite{focusing2014} $\parallel$ \cite{Efficient2015} $\parallel$ \cite{Resonant2017}) appear to establish that the net charge, mass, and envelope stiffness of a few species of viruses supports a weak resonance mode in the microwave spectrum, with a peak at roughly 8 GHz.

They appear to demonstrate that this allows a comparatively inconsequential electromagnetic field magnitude to produce mechanical stresses sufficient to crack the lipid envelope, destroying the virus.

By extending this work into the time-domain, pulsing the field at nanosecond scales, it appears to reduce the threshold to less than 1/Xth of all safety limits. Better yet, by scanning the focal point or beam , a significant area can be treated with a relatively small output power.

\cite{Efficient2015} test with various strains of Influenza A, we test with Coliphage T4; structural similarities with NCoV mean this

These authors above deserve all the credit for this finding; nothing in this work is even remotely novel.

{\Large \textbf{How is this better than the alternatives?}}

It penetrates tissue.

{\Large \textbf{Is it safe?}}

The consensus is that the environment not favorable to create such modes; damping from the surrounding fluids is too strong \cite{Vibrational2002}.

Quality in-vitro data supports this assertion. \cite{Cytogenetic2006} expose blood cells (a representative cell) to pulse power in precisely the regime required in this work; 8.2 GHz, 8 ns duration, 50 khz repetition rate, a whopping pulse power density of 250,000\Wsqm\footnote{computed from average power / duty cycle} (2500x the time-averaged power density safety limit), average power density 100\Wsqm (the safety limit), for 2 hours, finding no change in any of the measured quantities.

Similarly, \cite{DNA2004} use 8.8 GHz, 180 ns pulse width, peak power 65,000 W, repetition rate 50 Hz, exposure duration 40 min, and find genotoxicity purely due through the expected thermal mode.

[Foster 1987]

\footnote{These are cherry-picked.}

The literature reviews of \cite{ICNIRP2020} and \cite{C95} that they have conducted are far more exhaustive than ours.

Whether this is due to a specific feature of the virion or simply, we are unsure. The lipid bilayer of the virion differs in composition from that of the host cell.

@@

{\Large \textbf{How do we wield this sword?}}

Results seem to indicate that any region with a power density in the 7 to 9 GHz band greater than 300\Wsqm \ for 10 ns will be sterilized. This is not a particularly demanding requirement.

With modern semiconductor processes, it is trivial to produce

It is possible to create these conditions within human tissues; attenuation limits the safe treatment depth to about 3 cm.

\begin{autem}
	a
\end{autem}

%\centering {\color{red} \faHeart}

\clearpage

\printbibliography[heading=none, title={}]

\end{document}

### 2020-07-23 documents/supplemental.tex
Pamphlet

Method-of-moments solvers like NEC-2 are typical for simulating antennas. However, most commonly-available packages don't seem to handle multiple dielectric constants, such as the air and substrate for a patch antenna.

The impedance of an antenna over frequency can be determined in FDTD by:

\begin{itemize}
  \item Applying a gaussian pulse to a voltage source - in our case, applied to a via connecting the path (or probe)
  \item Running the simulation until the transients have all died out below some threshold, while logging the source voltage and current at each timestep
  \item Taking the fourier transform of the (real) excitation voltage and current (producing a complex result, mind you)
  \item Taking the ratio of the two complex spectra.
\end{itemize}

@@

Our implementation is in electronics/simple\_fdtd/runs/U.py.

@@

	\item A vinyl cutter was used to cut the openings in the top mylar cover slip.
	\item Cover plate machined from polycarbonate with a 1/16" two-flute carbide endmill, 24000 RPM, between 500 and 1000 mm/min, up to 1.5 mm step-down. G-code generated with MeshCAM. This seems to withstand the autoclave without any damage.
	\item Note: the tape preferentially sticks to the back liner, rather than the front.
	Rub the thing hard with a 
	Aluminum foil

@@

Making this device ourselves was a grave mistake that cost many lives. We should have used \cite{Straight}, a COTS version which we discovered halfway through.

@@

>>>>

Method-of-moments solvers like NEC-2 are the standard for simulating these sorts of antennas. However, most commonly-available packages don't seem to handle multiple dielectric constants, such as the air and substrate of a patch antenna.

The impedance of a structure over frequency can be determined in FDTD by:

\begin{itemize}
  \item Applying a gaussian pulse to a voltage source - in our case, applied to a via connecting the path (or probe)
  \item Running the simulation until the transients have all died out below some threshold, while logging the source voltage and current at each timestep
  \item Taking the fourier transform of the (real) excitation voltage and current (producing a complex result, mind you)
  \item Taking the magnitude of the ratio of the two complex spectra.
\end{itemize}

@@

Our implementation is in \ghfile{electronics/simple_fdtd/runs/U.py}.

@@

	\item A vinyl cutter was used to cut the openings in the top mylar cover slip.
	\item Frame machined from polycarbonate with a 1/16" two-flute carbide endmill, 24000 RPM, between 500 and 1000 mm/min, up to 1.5 mm step-down. G-code generated with MeshCAM. This seems to withstand the autoclave without any damage.
	\item Note: the tape preferentially sticks to the back liner, rather than the front.
	With both adhesive liners on, rub the thing hard with a rounded edge and rolling pin.
	Aluminum foil tape backing on the adhesive layer.
	Don't de-weed yet.

@@

Note that cutting many of these materials with a laser is a bad idea. The residue will

\begin{itemize}
	\item Tape mylar to a cardstock backing with masking tape on the sides. Cut mylar on plotter with InkCut. 175 g force. 
	\item Apply aluminum foil tape to the rear backing (with "3M" text) of the adhesive transfer tape. This supports the cut structures, without being cut itself.
	\item Stick the adhesive to the laser bed with Kapton, foil-side down. It's not a good idea to use masking tape; it'll catch fire.
	\item 
\end{itemize}

Making this device ourselves was a grave mistake that potentially cost many lives. We should have used \cite{Straight}, a COTS version which we discovered halfway through.

@@

\paragraph{Lessons learned:}

When trying to characterize the response to some process parameters (say, laser power), iteratively trying different parameters in series can be somewhat useful, as each trial informs the next. In this instance, we would try a speed and power, unstick the material from the bed, observe the result, decide on the course of action, and repeat. However, if it is possible to try many parameters in parallel just as fast as in series, (that is, in our case, make a coupon using [] that tries all reasonable values simultaneously), it would be very dumb not to do this.

We are very dumb.
